Actions are Bad, Mmkay

### 2018-11-24 paper/ms.tex
Update paper

We perform a set of three different simulations repeated for two of the Milky Way zoom-ins, \mi and \mf.\footnote{The number corresponds to the mass of the dark matter halo (here, $\sim 10^{12} \Msun$). The first letter stands for mass and the last letter is a unique identifier for the {\em initial conditions}.} The first assumes an axisymmetric potential

@@

>>>>

We perform a set of three different simulations repeated for two of the Milky Way zoom-ins, \mi and \mf.\footnote{The number corresponds to the mass of the dark matter halo (here, $\sim 10^{12} \Msun$). The first ``m'' stands for mass and the last letter is a unique identifier for the {\em initial conditions}.} The first assumes an axisymmetric potential and also implicitly a well-defined galactocentric frame. This first simulation shows that our integration technique respects the fact that in an axisymmetric potential actions are invariant and that our calculation of the actions does not imprint some artificial phase dependence in the actions.

@@

Rockstar import in gizmo_analysis is commented out
